% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Nick Pleatsikas}
\newcommand{\CVTitle}{Nick Pleatsikas's Resume}
\newcommand{\CVNote}{Resume compiled on {\today}}
\newcommand{\CVWebpage}{https://pleatsikas.me}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
Emeyville, CA 94608
\,\SubBulletSymbol\,
\href{mailto:nick@pleatsikas.me}
{nick@pleatsikas.me}
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%
%% Languages %%
%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}
Go, Python, Rust, C/C++

%%%%%%%%%%%%
%% Technologies %%
%%%%%%%%%%%%

\Section
{Technologies}
{Technologies}
{PDF:Technologies}
Git, Ansible, Chef, Terraform, Firebase, Redis, Docker, PostgreSQL

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{ucr.edu}
{\textbf{University of California, Riverside}},
Riverside, California

\Gap
\BulletItem
B.Sc., in
\href{https://engr.ucr.edu}
{Computer Engineering}
\hfill
\textit{Expected Jun 2020}
\begin{Detail}
\SubBulletItem
GPA: 3.80
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work\newline
Experience}
{Work Experience}
{PDF:WorkExperience}

\Entry
\href{https://minds.ai}
{\textbf{Minds.ai}},
Santa Cruz, CA

\Gap
\BulletItem
Software/Infrastructure Engineer
\hfill
\DatestampYMD{2016}{01}{05} --
\DatestampYMD{2019}{10}{01}
\begin{Detail}
\SubBulletItem
Created and deployed web services to assist in manual dataset and database tagging. Deployed
data preprocessing pipelines to ingest and categorize database tables for deep learning
backend. Completed during summer-long software engineering focused role.
\SubBulletItem
Created software in Python to bridge internal systems and automate infrastructure deployment.
See \textit{certcommander} and \textit{zoom-drive-connector} below for details on two
projects created during my employment.
\SubBulletItem
Provisioned Kubernetes deployment used to serve machine learning jobs to on-site hardware and Google Cloud platform.
\SubBulletItem
Introduced standardized provisioning, configuration management, and IaaS tools like Ansible, Chef, and Terraform into IT processes. Simplified maintenance and resource provisioning for
developers and administrators.
\end{Detail}
\BigGap

\Entry
\href{https://minds.ai}
{\textbf{Minds.ai}},
Santa Cruz, CA

\Gap
\BulletItem
Intern System Administrator
\hfill
\DatestampYMD{2015}{06}{15} --
\DatestampYMD{2015}{08}{15}
\begin{Detail}
\SubBulletItem
Deployed initial servers used by developers to create DL/ML software. Wrote basic management software and assisted in migrating from AWS to internal infrastructure.
\SubBulletItem
Implemented communication tools like Slack that improved overall accessibility for our distributed workforce.
\end{Detail}
\BigGap

%%%%%%%%%%%%%%%%%%%%%%%
%% Projects %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Projects}
{Projects}
{PDF:Projects}

\Entry
\href{https://github.com/opa-social}
{\textbf{Opa!}}: Go, Android, Redis, Firebase
\BulletItem
A business-oriented social media app design to help people find better business partners
at industry conferences built for my senior design project. I co-authored the service 
used to match users with each other. This service leverages classic machine learning 
techniques to generate matches and is built with technologies like Go, Redis, and Firebase.
\hfill
\BigGap

\Entry
\href{https://github.com/MrFlynn/stagelight}
{\textbf{stagelight}}: Go, Vue, C++, Python
\BulletItem
A proof-of-concept full stack application tying in both web and embedded systems technologies.
Stagelight connects a large number of low-power, low-cost wearable devices to a web control
panel with a fully-featured API. This project was written in Vue, Go, Python, and 
C++ utilizing technologies like Docker, Platform.io, and packet radio communication.
\hfill
\BigGap

\Entry
{\textbf{certcommander}}: Python
\BulletItem
A tool that automates the creation and renewal of SSL certificates using the ACME (Let's Encrypt) service using DNS challenges. Designed to be fully fault-tolerant; it can resume its previous state if it is restarted or crashes. Allows the user to define plugins to work with other DNS providers and send notifications to services like Slack.
\hfill
\BigGap

\Entry
\href{https://github.com/minds-ai/zoom-drive-connector}
{\textbf{zoom-drive-connector}}: Python
\BulletItem
An automation tool designed to automatically copy recorded meetings from Zoom to Google Drive.
\hfill
\BigGap

%%%%%%%%%%%%%%%
% Course Work %
%%%%%%%%%%%%%%%

\Section
{Relevant Course Work}
{Relevant Course Work}
{PDF:Relevant Course Work}

\BulletItem\textbf{CS111}: Discrete Structures \& Math
\BulletItem\textbf{CS141}: Intermediate Data Structures and Algorithms
\BulletItem\textbf{CS147}: GPU Programming
\BulletItem\textbf{CS164}: Computer Networks
\BulletItem\textbf{CS171}: Machine Learning and Data Mining
\BulletItem\textbf{CS172}: Information Retrieval

%%%%%%%%%%%%
%% Awards %%
%%%%%%%%%%%%
\Section
{Awards}
{Awards}
{PDF:Awards}

\BulletItem
BCOE Dean's List 
\hfill
\DatestampYMD{2016}{09}{23} --
\DatestampYMD{2017}{12}{15},
\DatestampYMD{2018}{04}{01} --
Present
\begin{Detail}
\Item
For achieving a GPA of 3.5 or higher per quarter.
\end{Detail}

\end{Body}
\end{document}